Convex Surrogates via Polyhedral Losses

### 2019-03-29 cvx-fin.tex
Jessie renamed and rewrote a bunch of things.  jessie-notes is my primary train of thoughht right now

For one-dimensional embeddings, the monotonicity property is extremely useful for lower bounds, as it is easy to check whether or not a given property is orderable.
However, for higher dimensions, we suggest that the optimality condition is also a promising direction for lower bounds.
To that end, we next derive a more specific necessary condition and use it to prove a lower bound on the ``abstain loss''.

@@

This provides the following recipe for both constructing losses and proving lower bounds.
First, take any level set and represent it as $\{p : Bp \geq 0\}$.
Now if $B$ has $k$ rows, search for a collection of $k$ vectors in $\reals^d$.
For any candidate $V$ (whose rows are the vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.

>>>>

For one-dimensional embeddings, the monotonicity property is extremely useful for lower bounds, as it is easy to check whether or not a given property is orderable.
\jessiet{Replace ''However'' with some other filler?}
However, for higher dimensions, we suggest that the optimality condition is also a promising direction for lower bounds.
To that end, we next derive a more specific necessary condition and use it to prove a lower bound on the ``abstain loss''.

@@

This provides the following recipe for both constructing losses and proving lower bounds.
First, take any level set and represent it as $\{p : Bp \geq 0\}$.
\jessiet{Is there any reason why $p \in \simplex$ would be implicit and not be required in $B$?  Asking more for the }
Now if $B$ has $k$ rows, search for a collection of $k$ vectors in $\reals^d$.
For any candidate $V$ (whose rows are the vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.

### 2019-03-29 jessie-writeup/jessie-notes.tex
Jessie renamed and rewrote a bunch of things.  jessie-notes is my primary train of thoughht right now

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, mathrsfs, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usepackage[margin=1.25in]{geometry}

\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
     citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}

@@

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\card}{\textbf{card}}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{notation}{Notation}

\begin{document}

\section{Notation and Definitions}

@@

\begin{definition}
Let $\Gamma:\P\toto\R$.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
\end{definition}
Informally, strip removes labels from the property.
\btw{Strip includes the boundaries of level sets / lower dimensional level sets.}

@@

\begin{definition}
	The elicitable property $\Gamma:\P\toto \reals^d$ is an \emph{d-embedding} of $\gamma: \P \toto \R$ if there exists an injection $\varphi:\R \to \reals^d$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. 
\end{definition}

@@

\section{Lemmas on the way}

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma:\P\toto\reals^d$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

@@

\section{Defining Embeddability}

@@

\newpage
\section{Definitions for paper}
\begin{definition}
	Let $\gamma:\Delta_\Y \toto \R$ and $\Gamma:\Delta_\Y \toto \R'$ be elicitable properties.
	The property $\gamma$ refines $\Gamma$ if, for all $r \in \R$, there is an $r' \in \R'$ so that $\gamma_r \subseteq \Gamma_{r'}$.
	[Additionally, there is at least one $r \in \R$ and $r' \in \R'$ such that $\gamma_r \subsetneq \Gamma_{r'}$.]
\end{definition}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsmath, amsthm, amssymb, graphicx, mathrsfs, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usepackage[margin=1.25in]{geometry}
\usetikzlibrary{calc}
\usepackage[colorlinks=true,breaklinks=true,bookmarks=true,urlcolor=blue,
     citecolor=blue,linkcolor=blue,bookmarksopen=false,draft=false]{hyperref}

@@

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\card}{\textbf{card}}
\newcommand{\simplex}{\Delta_\Y}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{notation}{Notation}
\newtheorem{claim}{Claim}

\begin{document}
\section{Drawing relationship between polytopes and subgradients}
\subsection{Starting with a loss}
If we are given a loss $L$ and set of embedded reports (possible minimizers of the expected loss over $\P$), we know that $r \in \Gamma(p) \iff 0 \in \partial_r L(r, p)$.
We can represent $\partial_r L(r,p)$ as a (closed) polytope given by by $\{x \in \reals^d : Ax \leq b \}$ for some $A$ and $b$.

If $\Gamma$ is $d$-\emph{minimally}-embeddable, then for some $r$ and $p$, the polytope $\partial_r L(r,p)$ should be full-dimensional in $\reals^d$.

\subsection{Thinking on the property}
Each level set of a finite elicitable property can be described as a convex polytope, and we can give this cell as $\{p \in \simplex : B^ip \geq 0 \}$, so that the matrix $B^i$ describes cell $i$.
Observe the subtle restriction that $p \in \simplex$.
This imposes nonnegativity constraints and the restriction that $\sum_i y_i =1$.

To take care of nonnegativity constraints, we can build them into $B$.
That is, each row of $B$ should describe a supporting hyperplane of the cell.

To ensure that $\sum_i y_i = 1$, we can then also add two rows to $B$ and the vector of inequalities.
That is, we can add $\ones^T p \leq 1$ and $-\ones^T p \leq -1$.

So, if $B^* = \begin{Bmatrix}
B \\
\ones^T \\
-\ones^T
\end{Bmatrix}$ 
and $0^* = \begin{Bmatrix}
\vec{0}\\
1\\
-1
\end{Bmatrix}$
, then we can see that $\{p \in \simplex: Bp \geq \vec{0} \} = \{p \in \reals^n : B^* p \geq 0^*\}$.

However, the equality constraints just restrict to a subset of the original cell (not restricted to the simplex), so we know that $\{p \in \reals^n : B^* p \geq 0^*\} \subseteq \{p \in \reals^n : B p \geq 0\}$, and focus on the matrix $B$ instead of $B^*$.

\jessie{The difference between nonnegativity constraints and summing to $1$ is that we can construct an affine transformation to reduce dimension by $1$, guarantee the sum adds to $1$?}

Consider that the dual of a polyhedron $C$ is another polyhedron $T$ where the vertices of $T$ are each associated with a facet of $C$.
Since our cells $C^i$ are described by a set of linear inequalities, we know the (nonredundant) vectors describing these inequalities are associated with a facet of $C^i$, and are therefore also associated with a vertex of $T^i$.

i.e. For each facet of $C$, there should be a vector $v_j \in \reals^n$ so that the facet is described by the halfspace $\{x : \inprod{v_j}{x} \leq b_{i,j} \}$ for each column of $B^i$ 
Therefore, if the cell $C^i$ is described by $k$ halfspaces, then there should be at least $k$ vectors $v_j$

\jessie{Do we know anything about a lower bound on the number of normals needed?  Combining with structure of the properties might help us prove bounds.}

\section{Sidebar}
Not sure if this proof is obvious, but I haven't convinced myself the following statement is true yet, although I think it should be (or at least some variation of it):
\begin{claim}
For a finite elicitable property $\Gamma: \simplex\to\R$, the level set $\Gamma_r$ is a convex polytope in $\simplex$.
\end{claim}

\section{Characterizing possible loss functions}
If we can find a set of normals $V$ and $B^i$ matrices describing each cell $C^i$ of the property $\Gamma$ such that $T(\cdot, y) := \{x : \inprod{V}{x} \geq B_{i} \}$ is nonempty for each column $i$ of $B$, then the polytopes form subgradient sets of a possible loss function eliciting $\Gamma$.
\jessie{Still unknown: does $V$ have to be the same across cells?}

However, the loss function eliciting $\Gamma$ is almost never unique; in fact, it is not the only loss \emph{embedding} $\Gamma$, either.
The loss over reports in the convex hull of the embedded reports may be unique, but outside the convex hull, can take on infinitely many values, so long as it does not ``go below'' the minimum value of the embedded report.
One question to ask here is, given a set of normals $V \in \reals^{k \times d}$, is there a set of matrices $\{B^i\}_{i=1}^{n}$ so that $T(r,y)$ is nonempty for all $r$and $y$?

\jessie{Another way to frame this is to fix the matrices $B$ and find such a set of normals $V$, but my hunch says that the first way might be easier for constructions, and this might be easier for bounds?}

\section{Case study: abstain}
\subsection{Constructing $B$ and $V$}
Consider the cell $C$ describing a level set.
For finite elicitable properties, we know $C$ is a convex polytope \jessie{See Claim 1}, and can thus be understood as either the convex hull as a finite set of distributions in $\simplex$, or as the intersection of a finite set of half spaces.

First, we should note that the matrix $B$ can be written one of many ways.
The only requirement of $B$ is that it describes the cell with nonnegativity constraints.
It should be noted, however, that we can normalize $B$ so that the max element in each row is $1$.
That way, we can look at the polar of the set $V$, and the set of subgradients should be a subset of $V^\circ$.

\jessie{Options: Start with $V$ and reverse-engineer $B$ or start with any $B$ describing the cell and find a $V$ that describes it?}

For abstain(1/2) on 4 outcomes, consider the set of normals $V = \{(1,1), (-1,1), (-1,-1), (1,-1)\}$, \jessie{representing each of the embedded points?}.
The polar $V^\circ$ is then a diamond inscribed in the convex hull of the normals.
\begin{figure}
\begin{center}
\begin{tikzpicture}[scale=3.0]
\draw[thick,->] (0,0) -- (0,-1);
\draw[thick,->] (0,0) -- (0,1);
\draw[thick,->] (0,0) -- (-1,0);
\draw[thick,->] (0,0) -- (1,0);

 \path[fill=gray, opacity=0.3] (0, 1) coordinate(p1) --  (-1, 0) coordinate(p2)
 -- (0, -1) coordinate(p3) --
 (1,0) coordinate(p4);

  \path[fill=blue, opacity=0.1] (1, 1) coordinate(c1) --  (-1, 1) coordinate(c2)
  -- (-1, -1) coordinate(c3) --
  (1,-1) coordinate(c4);
\end{tikzpicture}
\caption{$V^\circ$ in grey, $\conv(V)$ in blue.}
\label{fig:abstain-polar}
\end{center}
\end{figure}

For the abstain cell, we know that the matrix $B = \ones - 2I$ is unique up to scaling across rows. \jessie{I think... we haven't discussed or proved this.}
The polytopes $T(abs, \cdot)$ are then given as in Figure~\ref{fig:abstain-T-report-abs}.
\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, 1) --  (1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, 1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\caption{$T(abs, \cdot)$ for each $y \in \Y$.}
\label{fig:abstain-T-report-abs}
\end{figure}

However, this embedding gets a little trickier when thinking about the other cells.
For each report of an outcome $r$, we know the matrix $B^r$ is not unique.
For example, for $r_1$, we can see either

\[ B_1 = \begin{bmatrix}
1 & -1 & -1 & -1 \\
0 & 1 & 0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1 \\
\end{bmatrix} 
% 
\text{ or }
B_2 = 
\begin{bmatrix}
1 & -1 & -1 & -1 \\
1 & 0 & 1 & 1 \\
0 & 1 & 1 & 1 \\
1 & 1 & 0 & 1 \\
\end{bmatrix} 
\]

describe the cell properly (with nonnegativity constraints).
However, these two constructions of the $B$ yield different polytopes $T(r_1, \cdot)$ for nearly all of the outcomes. (See Figures~\ref{fig:abstain-T-report-r1-B1} and \ref{fig:abstain-T-report-r1-B2}.)
This begs the question of what a \emph{minimal} and \emph{maximal} set of such polytopes would look like.
(For abstain(1/2) with $n=4$, I have a proof sketch that shows that the $B_1$ matrix gives the minimal set of polytopes where $0 \in T(r_1, p) \iff p \in \Gamma_{r_1}$.
I can sketch that out at another time.)

\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\path[fill=black, opacity=0.3] (0, 1) --  (0,0) -- (1,0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\fill (-1,0) circle[radius=2pt];
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\fill (0,-1) circle[radius=2pt];
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_1$ matrix.}
\label{fig:abstain-T-report-r1-B1}
\end{figure}

\begin{figure}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\path[fill=black, opacity=0.3] (0, 1) --  (-1/2,1/2) -- (1/2, -1/2) -- (1,0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (-1/2, -1/2) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1, 0) ;
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.24\linewidth}
\begin{tikzpicture}[scale=1.5]
\draw[->] (0,0) -- (0,-1);
\draw[->] (0,0) -- (0,1);
\draw[->] (0,0) -- (-1,0);
\draw[->] (0,0) -- (1,0);
\draw[thick] (0, -1) --  (-1/2, -1/2) ;
\end{tikzpicture}
\end{minipage}
\caption{$T(r_1, \cdot)$ for each $y \in \Y$ using the $B_2$ matrix.}
\label{fig:abstain-T-report-r1-B2}
\end{figure}

\section{Misc. thoughts}
\begin{itemize}
	\item I did some work to try to characterize the ``minimal'' polytopes by considering the set of distributions $\P$ such that the cell $C = \conv(\P)$.
	However, I would call it far from a proof.
	Thoughts on whether this is worth pursuing farther would be appreciated?

	\item For abstain, we might want an extra, redundant normal $(0,0) \in V$ so that the vectors of $V$ are the embedded reports?  
	(Requires getting rid of assumption that normals are in general position.)

	\item If $T$ is related to $C$ by some strong enough notion of duality, can we use the affine dimension of $C$ to draw conclusions about the affine dimension of $T$ (and therefore embedding dimension of $\Gamma$?)

	\item Would it be plausible/desirable to write this as a convex program to find $V$ and $B$?

\end{itemize}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\section{Fun Trim proofs}
\subsection{Notation and Definitions}

@@

\jessiet{COmmented out definition of strip}
%\begin{definition}
%Let $\Gamma:\P\toto\R$.
%Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
%\end{definition}
%Informally, strip removes labels from the property.
%\btw{Strip includes the boundaries of level sets / lower dimensional level sets.}

@@

\begin{definition}
	The elicitable property $\Gamma:\P\toto \reals^d$ is a \emph{d-embedding} of $\gamma: \P \toto \R$ if there exists an injection $\varphi:\R \to \reals^d$ such that $\varphi(r) \in \Gamma(p) \iff r \in \gamma(p)$. 
\end{definition}

@@

\subsection{Lemmas on the way}

@@

\jessiet{Revisit this with the paper's definition of trim}
\begin{lemma}\label{lem:define-trim}
	Let $\Gamma:\P\toto\reals^d$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \trim(\Gamma)$.
\end{lemma}

@@

@@

### 2019-03-29 jessie-writeup/n9-not-3-embed.tex
Jessie renamed and rewrote a bunch of things.  jessie-notes is my primary train of thoughht right now

\newpage
\section{Post-submission thoughts}
\subsection{The mode}
\jessiet{For all the $\leq$ statements in here, there might be a reason they would have to be equalities, but I haven't been able to think it fully through/prove it, so they are in here as inequalities for now.}
\begin{conjecture}
	The normals constructing a tight H-rep for a cell for the mode must be linearly independent
\end{conjecture}
\begin{proof}
  Consider the matrix describing the cell for outcome $n$...

@@

  Now for each column $B_i^{(n)}$ of $B^{(n)}$, we must have a set of normals such that for each normal $j$, we must have $\inprod{V_j}{x} = B_{i,j}$ in order for the halfspace representation to be tight.
  Let us write the polytope $T_i := \{x \in \reals^d : Vx \leq B_i \}$ as the feasible polytope for the H-rep of the property.
  In order for $\{x \in T_n : \inprod{V_j}{x} = 1 \}$ to be nonempty for all $V_j$, we assert the normals $V_j$ must all be linearly independent.

@@

  To see this, first consider that if $V_2 = -V_1$ , then one of these constraints for the polytope $T_n$ is redundant.
  Therefore these normals do not form a tight $H$-rep since for (WLOG) $V_2$, the halfspace represented by $\{x : \inprod{V_2}{x} \leq 1 \}$ is a (strict since none of the normals can be $0$) subset of the halfspace $\{x : \inprod{V_1}{x} \leq 1 \}$.

@@

  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_i$s, then $\inprod{V_{\Laughey}}{x} = \sum_{i\neq \Laughey} \inprod{\lambda_i V_i}{x} \geq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$.

  If $\lambda_n= -1$, we contradict the tightness of $T_n$ shown above. 
  Otherwise, we contradict the tightness of $T_i$ since there is no constraint such that $\inprod{V_{\Laughey}}{x} = -1$ given the tightness of the other constraints.

>>>>

\newpage
\section{Post-submission thoughts}
\subsection{The mode}
\jessiet{For all the $\leq$ statements in here, there might be a reason they would have to be equalities, but I haven't been able to think it fully through/prove it, so they are in here as inequalities for now.}
\begin{conjecture}
	The normals constructing a tight H-rep for a cell for the mode must be linearly independent
\end{conjecture}
\begin{proof}
  Consider the matrix $B^{(n)} \in \reals^{n-1 \times n}$ describing the cell for outcome $n$...

@@

  Now for each column $B_i^{(n)}$ of $B^{(n)}$, we must have a set of normals such that for each normal $j$, we must have $\inprod{V_j}{x} = B_{i_j}$ in order for the halfspace representation to be tight.
  Let us write the polytope $T_i := \{x \in \reals^d : Vx \leq B_i \}$ as the feasible polytope for the H-rep of the property.
  In order for $\{x \in T_n : \inprod{V_j}{x} = 1 \}$ to be nonempty for all $V_j$, we assert the normals $V_j$ must all be linearly \jessie{affinely?} independent.

@@

  To see this, first consider that if $V_2 = -V_1$, then (for $n > 3$) both polytopes $T_1$ and $T_2$ will be empty, as the constraint $\inprod{v_1}{x} \leq 0$ cannot be satisfied alongside the constraint $\inprod{v_2}{x} \leq -1 \iff \inprod{v_1}{x} \geq 1$ for $T_2$, and we reach a similar contradiction for $T_1$.

@@

%  The following is wrong.  I think it's close ish, but definitely wrong.
%  Given the tightness constraints, if $V_{\Laughey}$ is a linear combination of $V_j$s, then $\inprod{V_{\Laughey}}{x} = \sum_{j\neq \Laughey} \inprod{\lambda_j V_j}{x} \leq 0 + 0 + \ldots + 0 + \lambda_n = \lambda_n$ by the restriction that $x \in T_n$.
%  	
%  If $\lambda_n= -1$, we contradict the tightness of $T_{\Laughey}$ shown above. 
%  Otherwise, we contradict the tightness of $T_i$ since there is no constraint such that $\inprod{V_{\Laughey}}{x} = -1$ given the tightness of the other constraints.
